Normalized Coherence

### 2019-09-18 Analysis/Normalized_Coherence.Rmd
Make the min network size a setting

```{r}
# Option for number of msig pathways to take from each category
num_msig = 10
# Option for number of random networks to generate (Will generate num_rand-1 networks)
num_rand = 11
# Construct file name to save the results
run <- 1 # Placeholder for the run ID
fileNameOut <- file.path("./data/Coherence_Results/", paste0("coherence_msig_", num_msig, "_rand_", num_rand, "_", run, ".csv"))
```

@@

```{r}
# [??? What this function does? Write roxygen help]
slopes_from_edges = function(edges) {
  edges %>% filter(Internal != 0)  %>%
  group_by(Disease, Category) %>% mutate(Count = n()) %>% group_by(Disease, Category, Count) %>%
  do({
    mod = lm(sqrt(External) ~ sqrt(Internal)-1, data = .)
    data.frame(Slope= coef(mod)[1])
  }) %>% arrange(Slope) %>% filter(Count>4)
}
```

The above function takes internal and external edges from each gene for each disease and calculates the total number of genes and the slope of internal vs. external edges. Genes with zero internal edges are filtered and diseases with less than 5 non-zero internal edges are filtered.

>>>>

```{r}
# Option for number of msig pathways to take from each category
num_msig = 10
# Option for number of random networks to generate (Will generate num_rand-1 networks)
num_rand = 101
# Minimum number of genes having non-zero internal edges for a network to be processed
num_genes = 10
# Construct file name to save the results
run <- 1 # Placeholder for the run ID
fileNameOut <- file.path("./data/Coherence_Results/", paste0("coherence_msig_", num_msig, "_rand_", num_rand, "_", run, ".csv"))
```

@@

```{r}
# [??? What this function does? Write roxygen help]
slopes_from_edges = function(edges) {
  edges %>% filter(Internal != 0)  %>%
  group_by(Disease, Category) %>% mutate(Count = n()) %>% group_by(Disease, Category, Count) %>%
  do({
    mod = lm(sqrt(External) ~ sqrt(Internal)-1, data = .)
    data.frame(Slope= coef(mod)[1])
  }) %>% arrange(Slope) %>% filter(Count > num_genes)
}
```

The above function takes internal and external edges from each gene for each disease and calculates the total number of genes and the slope of internal vs. external edges. Genes with zero internal edges are filtered and diseases with less than `r num_genes` non-zero internal edges are filtered.
